What does it take to create with domain-appropriate tools?

### 2020-05-15 convivial-2020/acm-style/ccs20-acm.tex
All day --> ACM style. I hate BibTeX. heck maybe i just hate latex altogether

\documentclass[english,submission]{programming}
\usepackage[
backend=biber,
style=alphabetic
]{biblatex} % Use Biblatex
\addbibresource{../refs.bib}

@@

@@

\paperdetails{
  perspective=art,
  area={Domain-specific programming, visual programming, self-sustaining systems}
}

@@

\input{../manuscript.tex}

\printbibliography
\end{document}

>>>>

\documentclass[sigconf,screen]{acmart}
\usepackage{listings}

\citestyle{acmauthoryear}

@@

\setcopyright{acmlicensed}
\acmPrice{15.00}
\acmDOI{10.1145/3397537.3397549}
\acmYear{2020}
\copyrightyear{2020}
\acmSubmissionID{prog20ccs-id8-p}
\acmISBN{978-1-4503-7507-8/20/03}
\acmConference[<Programming'20> Companion]{Companion Proceedings of the 4th International Conference on the Art, Science, and Engineering of Programming}{March 23--26, 2020}{Porto, Portugal}
\acmBooktitle{Companion Proceedings of the 4th International Conference on the Art, Science, and Engineering of Programming (<Programming'20> Companion), March 23--26, 2020, Porto, Portugal}

@@

@@

\input{manuscript-acm.tex}

\bibliography{../refs.bib}

\end{document}

### 2020-05-15 convivial-2020/acm-style/manuscript-acm.tex
All day --> ACM style. I hate BibTeX. heck maybe i just hate latex altogether

\hypertarget{the-system}{%
\section{\texorpdfstring{The Id{}
system}{The  system}}\label{the-system}}

@@

\hypertarget{as-html-tables}{%
\subsection{\texorpdfstring{Id{} as HTML
tables}{ as HTML tables}}\label{as-html-tables}}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{../orom-html-cropped.png}
  \caption{Part of Id{}/HTML: Obj-dicts are rendered as resizable tables, which reference
           each other through numerical IDs. \label{fig:orom-html}}
\end{figure}

@@

\hypertarget{as-svg-trees}{%
\subsection{\texorpdfstring{Id{} as SVG
trees}{ as SVG trees}}\label{as-svg-trees}}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{../orom-svg-cropped.png}
  \caption{Part of Id{}/SVG: Obj-dicts are moveable and resizable nested boxes,
           referencing each other via \emph{real arrows}.\label{fig:orom-svg}}
\end{figure}

@@

My original flat, tabular representation in Id{}/HTML did support a
single level of such ``extensional functions'', but no more. In other
words, the output of such a mapping could not be a further mapping
itself. This was problematic because vtables, conceptually, have two
levels of such nesting: the top-level fields, and the ``methods
dictionary'' which contains its own input-output pairs. To distinguish
between these, I actually stored method mappings with an ad-hoc ``-''
character (Figure\textasciitilde{}\ref{fig:method-hyphens}).

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{../method-hyphens.png}
  \caption{Id{}/HTML: use of hyphenated \texttt{-lookup} to signify a \emph{method} called
           \texttt{lookup} instead of a property like \texttt{vtable}. \label{fig:method-hyphens}}
\end{figure}

@@

\hypertarget{the-system-as-a-part-of-the-solution}{%
\section{\texorpdfstring{The Id{} system as a part of the
solution}{The  system as a part of the solution}}\label{the-system-as-a-part-of-the-solution}}

>>>>

\hypertarget{the-id-system}{%
\section{The Id system}\label{the-id-system}}

@@

\hypertarget{id-as-html-tables}{%
\subsection{Id as HTML tables}\label{id-as-html-tables}}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{orom-html.png}
  \caption{Part of Id{}/HTML: Obj-dicts are rendered as resizable tables, which reference
           each other through numerical IDs. \label{fig:orom-html}}
\end{figure}

@@

\hypertarget{id-as-svg-trees}{%
\subsection{Id as SVG trees}\label{id-as-svg-trees}}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{orom-svg.png}
  \caption{Part of Id{}/SVG: Obj-dicts are moveable and resizable nested boxes,
           referencing each other via \emph{real arrows}.\label{fig:orom-svg}}
\end{figure}

@@

My original flat, tabular representation in Id{}/HTML did support a
single level of such ``extensional functions'', but no more. In other
words, the output of such a mapping could not be a further mapping
itself. This was problematic because vtables, conceptually, have two
levels of such nesting: the top-level fields, and the ``methods
dictionary'' which contains its own input-output pairs. To distinguish
between these, I actually stored method mappings with an ad-hoc ``-''
character (Figure\textasciitilde{}\ref{fig:orom-html}).

@@

@@

\hypertarget{the-id-system-as-a-part-of-the-solution}{%
\section{The Id system as a part of the
solution}\label{the-id-system-as-a-part-of-the-solution}}
